---
title: "NFL Sim Draft Value"
author: "Brandon"
date: "3/19/2020"
output: html_document
---

```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_knit$set(root.dir = "~/Documents/fantasy-football/data")
```
```{r, include=FALSE}
#loading packages
for (pkg in c("tidyverse", "tidytext", "reshape2", 
              "ggplot2")) {library(pkg, character.only = TRUE)}
# pulling the data 
raw_data <- read_csv("sim-data.csv") 
`%notin%` <- Negate(`%in%`)
```

# BEST OVERALL RANKINGS 

```{r top_ranking_QBs }
raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "RB" | Position == "WR") %>% 
  arrange(Rk)
```
```{r top_ranking_RBs }
raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "RB") %>% 
  arrange(-fppg)
```
```{r top_rankings_WRs }
raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "WR") %>% 
  arrange(-fppg)
```

## BEST AVAILABLE (REMOVES DRAFTED PLAYERS AT POSITION, FILTERS TOP-10 FOR POSITION)

```{r best_av_qb}
drafted_QBs <- "Lamar Jackson|Deshaun Watson|Dak Prescott|Patrick Mahomes|Kyler Murray|Russell Wilson|Aaron Rodgers|Daniel Jones|Carson Wentz"
best_av_qb <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "QB" & FPts > 70) %>% 
  filter(Status == "FA") %>% 
  filter(!grepl(drafted_QBs, Player)) %>% 
  top_n(10, fppg) %>% 
  #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_qb$FPts); sd(best_av_qb$FPts)   
mean(best_av_qb$fppg); sd(best_av_qb$fppg); best_av_qb 
```

```{r best_av_rb}
drafted_RBs <- "Christian McCaffrey|Saquon Barkley|Ezekiel Elliott|Dalvin Cook|Josh Jacobs|Derrick Henry|Alvin Kamara|Joe Mixon|Nick Chubb|Aaron Jones|Austin Ekeler|Miles Sanders|Leonard Fournette|Marlon Mack"
best_av_rb <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "RB" & FPts > 70) %>% 
  filter(Status == "FA") %>%
  filter(!grepl(drafted_RBs, Player)) %>% 
  #top_n(10, fppg) %>% 
  #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_rb$FPts); sd(best_av_rb$FPts)   
mean(best_av_rb$fppg); sd(best_av_rb$fppg); best_av_rb   
```
```{r best_av_wr}
drafted_WRs <- "Michael Thomas|DeAndre Hopkins|Tyreek Hill|Chris Godwin|Cooper Kupp|Davante Adams|Stefon Diggs|Odell Beckham Jr.|Mike Evans|DJ Moore|Amari Cooper|Kenny Golladay"
best_av_wr <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "WR" & FPts > 20) %>% 
  filter(Status == "FA") %>%
  filter(!grepl(drafted_WRs, Player)) %>% 
  #top_n(10, fppg) %>% 
  arrange(-fppg)
mean(best_av_wr$FPts); sd(best_av_wr$FPts)   
mean(best_av_wr$fppg); sd(best_av_wr$fppg); best_av_wr   
```
```{r best_av_te}
drafted_TEs <- "George Kittle"
best_av_te <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "TE") %>% 
  filter(Status == "FA") %>%
  filter(!grepl(drafted_TEs, Player)) %>% 
  top_n(10, fppg) %>%
  #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_te$FPts); sd(best_av_te$FPts)   
mean(best_av_te$fppg); sd(best_av_te$fppg); best_av_te   
```
```{r best_av_def}
defensive_positions <- "DT|DE|LB|CB"
drafted_DEF <- "No Names Yet"
best_av_def <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(grepl(defensive_positions, Position)) %>% 
  #filter(Status == "FA") %>%
  filter(!grepl(drafted_DEF, Player)) %>% 
  top_n(10, fppg) %>% 
  #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_def$FPts); sd(best_av_def$FPts)   
mean(best_av_def$fppg); sd(best_av_def$fppg); best_av_def

drafted_LB <- "No Names Yet"
best_av_lb <- raw_data %>% 
  rename(fppg = `FP/G`) %>% filter(Position == "LB") %>%
  #filter(grepl(defensive_positions, Position)) %>% #filter(Status == "FA") %>%
  filter(!grepl(drafted_LB, Player)) %>% top_n(10, FPts) %>% #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_lb$FPts); sd(best_av_lb$FPts)   
mean(best_av_lb$fppg); sd(best_av_lb$fppg); best_av_lb

drafted_CB <- "No Names Yet"
best_av_cb <- raw_data %>% 
  rename(fppg = `FP/G`) %>% filter(Position == "CB") %>%
  #filter(grepl(defensive_positions, Position)) %>% #filter(Status == "FA") %>%
  filter(!grepl(drafted_CB, Player)) %>% top_n(10, fppg) %>% #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_cb$FPts); sd(best_av_cb$FPts)   
mean(best_av_cb$fppg); sd(best_av_cb$fppg); best_av_cb

drafted_S <- "No Names Yet"
best_av_sfty <- raw_data %>% 
  rename(fppg = `FP/G`) %>% filter(Position == "S") %>%
  #filter(grepl(defensive_positions, Position)) %>% #filter(Status == "FA") %>%
  filter(!grepl(drafted_S, Player)) %>% top_n(10, fppg) %>% #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_sfty$FPts); sd(best_av_sfty$FPts)   
mean(best_av_sfty$fppg); sd(best_av_sfty$fppg); best_av_sfty

drafted_DE <- "No Names Yet"
best_av_de <- raw_data %>% 
  rename(fppg = `FP/G`) %>% filter(Position == "DE") %>%
  #filter(grepl(defensive_positions, Position)) %>% #filter(Status == "FA") %>%
  filter(!grepl(drafted_DE, Player)) %>% top_n(10, fppg) %>% #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_de$FPts); sd(best_av_de$FPts)   
mean(best_av_de$fppg); sd(best_av_de$fppg); best_av_de

drafted_DT <- "No Names Yet"
best_av_dt <- raw_data %>% 
  rename(fppg = `FP/G`) %>% filter(Position == "DT") %>%
  #filter(grepl(defensive_positions, Position)) %>% #filter(Status == "FA") %>%
  filter(!grepl(drafted_DT, Player)) %>% top_n(10, fppg) %>% #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_dt$FPts); sd(best_av_dt$FPts)   
mean(best_av_dt$fppg); sd(best_av_dt$fppg); best_av_dt

```
```{r best_av_kkr}
drafted_Kkrs <- "No Names Yet"
best_av_kkr <- raw_data %>% 
  rename(fppg = `FP/G`) %>%
  filter(Position == "K" & FPts > 100) %>% 
  filter(Status == "FA") %>%
  filter(!grepl(drafted_Kkrs, Player)) %>% 
  top_n(10, fppg) %>% 
  #top_n(10, FPts) %>% 
  arrange(-fppg)
mean(best_av_kkr$FPts); sd(best_av_kkr$FPts)   
mean(best_av_kkr$fppg); sd(best_av_kkr$fppg); best_av_kkr   
```

```{r best_available_sum, results = 'asis' }
best_available_sum <- as_tibble(data.frame(
  "position" = c("QB", "RB", "WR", "TE", "K", "DEF", "LB", "CB", "S", "DE", "DT"),
  "fpts" = c(mean(best_av_qb$FPts), mean(best_av_rb$FPts), 
             mean(best_av_wr$FPts), mean(best_av_te$FPts), 
             mean(best_av_kkr$FPts),
             mean(best_av_def$FPts), mean(best_av_lb$FPts), 
             mean(best_av_cb$FPts), mean(best_av_sfty$FPts), 
             mean(best_av_de$FPts), mean(best_av_dt$FPts)), 
  "fptsSD" = c(sd(best_av_qb$FPts), sd(best_av_rb$FPts), 
               sd(best_av_wr$FPts), sd(best_av_te$FPts), 
               sd(best_av_kkr$FPts),
               sd(best_av_def$FPts), sd(best_av_lb$FPts),
               sd(best_av_cb$FPts), sd(best_av_sfty$FPts),
               sd(best_av_de$FPts), sd(best_av_dt$FPts)),
  "fppg" = c(mean(best_av_qb$fppg), mean(best_av_rb$fppg), 
             mean(best_av_wr$fppg), mean(best_av_te$fppg), 
             mean(best_av_kkr$fppg),
             mean(best_av_def$fppg), mean(best_av_lb$fppg),
             mean(best_av_cb$fppg), mean(best_av_sfty$fppg),
             mean(best_av_de$fppg), mean(best_av_dt$fppg)),
  "ffpgSD" = c(sd(best_av_qb$fppg), sd(best_av_rb$fppg), 
               sd(best_av_wr$fppg), sd(best_av_te$fppg), 
               sd(best_av_kkr$fppg),
               sd(best_av_def$fppg), sd(best_av_lb$fppg),
               sd(best_av_cb$fppg), sd(best_av_sfty$fppg),
               sd(best_av_de$fppg), sd(best_av_dt$fppg))))
best_available_sum %>% arrange(-fppg) 
```
This table shows the mean and SD values for the top-10 available positions. The higher the mean, the higher overall contribution that the position will give at this point in the draft. The higher SD, the more potential value is available at the position. This latter claim is based on the assumption that the more variance there is, the more important drafting the position right now is. 

```{r}
for_heatmap <- data.frame(
  "position" = c("QB", "RB", "WR", "TE", "K", "DEF", "LB", "CB", "S", "DE", "DT"),
  "fpts" = c(mean(best_av_qb$FPts), mean(best_av_rb$FPts), 
             mean(best_av_wr$FPts), mean(best_av_te$FPts), 
             mean(best_av_kkr$FPts),
             mean(best_av_def$FPts), mean(best_av_lb$FPts), 
             mean(best_av_cb$FPts), mean(best_av_sfty$FPts), 
             mean(best_av_de$FPts), mean(best_av_dt$FPts)), 
  "fptsSD" = c(sd(best_av_qb$FPts), sd(best_av_rb$FPts), 
               sd(best_av_wr$FPts), sd(best_av_te$FPts), 
               sd(best_av_kkr$FPts),
               sd(best_av_def$FPts), sd(best_av_lb$FPts),
               sd(best_av_cb$FPts), sd(best_av_sfty$FPts),
               sd(best_av_de$FPts), sd(best_av_dt$FPts)),
  "fppg" = c(mean(best_av_qb$fppg), mean(best_av_rb$fppg), 
             mean(best_av_wr$fppg), mean(best_av_te$fppg), 
             mean(best_av_kkr$fppg),
             mean(best_av_def$fppg), mean(best_av_lb$fppg),
             mean(best_av_cb$fppg), mean(best_av_sfty$fppg),
             mean(best_av_de$fppg), mean(best_av_dt$fppg)),
  "ffpgSD" = c(sd(best_av_qb$fppg), sd(best_av_rb$fppg), 
               sd(best_av_wr$fppg), sd(best_av_te$fppg), 
               sd(best_av_kkr$fppg),
               sd(best_av_def$fppg), sd(best_av_lb$fppg),
               sd(best_av_cb$fppg), sd(best_av_sfty$fppg),
               sd(best_av_de$fppg), sd(best_av_dt$fppg))) 
for_heatmap <- for_heatmap %>% 
  mutate(fpts_norm = fpts, fptsSD_norm = fptsSD, fppg_norm = fppg, ffpgSD_norm = ffpgSD) %>% 
  mutate_at(scale, .vars = vars(c("fpts_norm", "fptsSD_norm", "fppg_norm", "ffpgSD_norm"))) %>% 
  mutate(fpts_norm = (fpts_norm-min(fpts_norm))/(max(fpts_norm)-min(fpts_norm)),
         fptsSD_norm = (fptsSD_norm-min(fptsSD_norm))/(max(fptsSD_norm)-min(fptsSD_norm)),
         fppg_norm = (fppg_norm-min(fppg_norm))/(max(fppg_norm)-min(fppg_norm)),
         ffpgSD_norm = (ffpgSD_norm-min(ffpgSD_norm))/(max(ffpgSD_norm)-min(ffpgSD_norm))
         )

for_heatmap$position <- with(for_heatmap, reorder(position, fppg_norm))
for_heatmap <- for_heatmap %>% 
  select(-fpts, -fptsSD, -fppg, -ffpgSD)  
  #select(-fpts_norm, -fptsSD_norm, -fppg_norm, -ffpgSD_norm)

melt(for_heatmap) %>% 
  ggplot(aes(variable, position)) + 
         geom_tile(aes(fill=value)) + theme_minimal() +
  scale_fill_gradient(low = "steel blue", high = "orange") +  
  labs(title = "Available Value by Position ",
       subtitle = "For Next Best 10 Players by Position (Lighter Color = More Value)") +
  theme(plot.title = element_text(size=14, hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size=10, hjust = 0.5),
                          axis.title.x = element_blank(),
                          axis.title.y = element_blank()) 
```

# EXISTING VALUE CALCULATORS 

```{r}
# contracts 
paid15m <- c("Patrick Mahomes|Christian McCaffrey|Lamar Jackson|Saquon Barkley|Michael Thomas|DeAndre Hopkins|Ezekiel Elliott|Deshaun Watson")
paid14m <- c("Alvin Kamara|Dalvin Cook|Kyler Murray|Dak Prescott|Josh Allen|Josh Jacobs|Derrick Henry|Joe Mixon")
paid13m <- c("Nick Chubb|Tyreek Hill|Aaron Jones|Chris Godwin|Russell Wilson|Cooper Kupp|Davante Adams")
paid12m <- c("Aaron Rodgers|Austin Ekeler|George Kittle")
paid11m <- c("zczyzcz")
paid10m <- c("zczyzcz")
paid9m <- c("zczyzcz")
paid8m <- c("zczyzcz")
paid7m <- c("zczyzcz")
paid6m <- c("zczyzcz")
paid5m <- c("zczyzcz")
paid4m <- c("zczyzcz")
paid3m <- c("zczyzcz")
paid2m <- c("zczyzcz")
paid1m <- c("zczyzcz")

value_matrix <- raw_data %>% 
  rename(player = Player, ttl_fpts = FPts, fppg = `FP/G`, 
         rank = Rk, position = Position) %>% 
  select(rank, player, ttl_fpts, fppg) %>% 
  # apply contract totals 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid15m), yes = "15", no = NA)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid14m), yes = "14", no = contract)) %>%
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid13m), yes = "13", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid12m), yes = "12", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid11m), yes = "11", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid10m), yes = "10", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid9m), yes = "9", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid8m), yes = "8", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid7m), yes = "7", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid6m), yes = "6", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid5m), yes = "5", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid4m), yes = "4", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid3m), yes = "3", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid2m), yes = "2", no = contract)) %>% 
  mutate(contract = ifelse(test = str_detect(string = player, 
                     pattern = paid1m), yes = "1", no = contract)) %>% 
  mutate(contract = as.numeric(contract)) %>% 
  # apply value totals 
  mutate(fppg_value = round(fppg / contract, 3), 
         ttl_fpts_value = round(ttl_fpts / contract, 3)) %>% 
  # standardize values 
  drop_na(fppg_value) %>% 
  #mutate_at(scale, .vars = vars(c("fppg_value"))) %>%
  mutate(fppg_norm = round((fppg_value-min(fppg_value))/(max(fppg_value)-min(fppg_value)), 3)) %>% 
  mutate(ttl_fpts_norm = 
  round((ttl_fpts_value-min(ttl_fpts_value))/(max(ttl_fpts_value)-min(ttl_fpts_value)), 3)) %>% 
  select(-contract) %>% 
  filter(rank < 400) %>%
  arrange(-fppg_value); value_matrix
  #arrange(-ttl_fpts_value); value_matrix
```

```{r}
drafted_players <- unlist(str_split(c(drafted_QBs, drafted_RBs, drafted_WRs, drafted_TEs, drafted_Kkrs, 
                     drafted_CB, drafted_DE, drafted_DT, drafted_LB, drafted_S), "\\|"))

ggplot(melt(value_matrix %>%
              mutate(player = reorder(player, fppg_norm)) %>%
              #top_n(30) %>% 
              #filter(player %in% drafted_players) %>% 
              #filter(player != drafted_players) %>%
              #filter(rank < 50) %>% 
              select(player, fppg_norm, ttl_fpts_norm)), 
       aes(variable, player, fill= value)) + geom_tile() +
  theme_minimal() +
  labs(title = "Best Player Value (FFPG/Contract)") +
  scale_fill_gradient(low = "steel blue", high = "orange") +
  theme(plot.title = element_text(size=14, hjust = 0.5, face = "bold"),
        plot.subtitle = element_text(size=10, hjust = 0.5),
                          axis.title.x = element_blank(),
                          axis.title.y = element_blank()) 
```

```{r}




```






```{r}
# create a value matrix
value_matrix <- raw_data %>% 
  rename(player = Player, tfpts = FPts, fppg = `FP/G`, 
         rank = Rk, position = Position) %>% 
  select(rank, player, tfpts, fppg) %>% 
  mutate(p1_8 = fppg / 15) %>% mutate(p9_16 = fppg / 14) %>% 
  mutate(p17_24 = fppg / 13) %>% mutate(p25_32 = fppg / 12) %>% 
  mutate(p33_40 = fppg / 12) %>% mutate(p41_48 = fppg / 11) %>% 
  mutate(p49_56 = fppg / 10) %>% mutate(p57_64 = fppg / 9) %>% 
  mutate(rd3 = fppg / 9) %>% mutate(rd4 = fppg / 8) %>% 
  mutate(rd5 = fppg / 7) %>% mutate(rd6 = fppg / 6) %>% 
  mutate(rd7 = fppg / 5) %>% mutate(rd8 = fppg / 4) %>% 
  mutate(rd9 = fppg / 4) %>% mutate(rd10 = fppg / 3.5) %>% 
  mutate(rd11 = fppg / 3) %>% mutate(rd12 = fppg / 3) %>% 
  mutate(rd13 = fppg / 3) %>% mutate(rd14 = fppg / 3) %>% 
  mutate(rd15 = fppg / 3) %>% mutate(rd16 = fppg / 2) %>%
  mutate(rd17 = fppg / 2) %>% mutate(rd18 = fppg / 2) %>%
  mutate(rd19 = fppg / 2) %>% mutate(rd20 = fppg / 2) %>%
  mutate(rd21 = fppg / 1) %>% mutate(rd22 = fppg / 1) %>%
  mutate(rd23 = fppg / 1) %>% mutate(rd24 = fppg / 1) %>%
  mutate(rd25 = fppg / 1) %>% mutate(rd26 = fppg / 1) %>%
  mutate(rd27 = fppg / 1) %>% mutate(rd28 = fppg / 1) %>%
  mutate(rd29 = fppg / 1) %>% mutate(rd30 = fppg / 1) %>%
  mutate(rd31 = fppg / 1) %>% mutate(rd32 = fppg / 1) 
value_matrix
```
